\section{Report structure}
The report will be split into several chapters which each explain the different areas that have been explored to fulfil the requirements of this assignment. In Chapter \ref{chap:general} the general concepts will be discussed. Chapter \ref{chap:physical} will go into the physical layer in depth, which defines the rules of the data transmission itself and how it should handle this data regarding the upper layer. Chapter \ref{chap:dll} will contain an overview of the data link layer, which explains concepts around the frame, flow control and error control. Chapter \ref{chap:transport} will explain the workings behind the process-to-process communication. Utilisation and concepts of the application programming interface which acts as the easy-to-use feature of the protocol stack is explained in Chapter \ref{chap:api}. The backbone which control the flow of data between layers is explained in Chapter \ref{chap:backbone}. Chapter \ref{chap:test} will explain the test tool that have been developed to test each layer separately for stability issues. Experiments conducted will be held in Chapter \ref{chap:experiments}. A discussion of the process, solutions, and the results takes place in Chapter \ref{chap:discussion}. The conclusion will located in Chapter \ref{chap:conclusion}.

%Along with this report a CD will be attached, which contain all material produced during this process.
Furthermore, a CD which contains all the materials produced during this process will be attached to the report. The source and the distributed application will be included on the CD as well.