\chapter*{Preface}\addcontentsline{toc}{chapter}{Preface}
This report was made during our fourth semester on the way to becoming engineers. The group has worked 
together to fine results on third semester, and thus agreed on some things we wanted to change compared 
to that. 

The first change was, that instead of going for the ``overkill'', we wanted to focus on finishing the 
project. We all have access to lots of practical work in our spare time projects, so in this project we 
wanted to go into the engineering skills in depth.
Individually we wanted to explore working in new areas and to dig deep and specialize. Therefore we 
wanted to split the project into smaller, more manageable parts and the participants in the group then 
picked their task of interest.

We agreed, that the system should be thoroughly tested, keeping in mind the difference between testing 
and debugging. Since a system can only be tested once it performs, our priority was to achieve a fully 
working and well documented system.

On the former semesters, different models for group corporation has been tried out and though 
interesting, the group felt a need to abandon the fine models and instead go for mutual reliance and 
trusting, that we are all working for a joint purpose. This meant that the advanced management tools and 
role based models were replaced by a simple log, and a will to finish the project.

All this together formed a decision about keeping the project simple and not decide on the application of 
the system, but simply build a robust and well performing system ready for others to facilitate.
We believe to have succeeded in these objectives.

\vspace*{0.5cm}
\begin{flushright}
Kent, Rudi, Kim, Alexander, Frederik and Leon
\end{flushright}